---
title: "Grey's Anatomy"
author: "Charles Schumacher"
date: "Thursday, Oct 25, 2018"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
library(knitr)
path <- "PATH"

setwd(path)
read_chunk("ga_net.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Exponential Random Graph Modeling

In this lab, we work with the romantic relationship data
compiled from the TV show "Grey's Anatomy" to answer questions
about the different levels of sexual activity among men and
women on the show.

Thanks to Benjamin Lind for the data and examples.

### Loading libraries

```{r C1, results="hide", warning=FALSE, message=FALSE}
```

### Setting path and loading utilities and the network

```{r C2}
```

### Showing the network

```{r C3}
```

## Convert the graph to a ```network``` object 

Use the ```asNetwork``` function from the intergraph library.

```{r C4}
```

## Model 1: Edges and sex

Construct an ERGM model with the edges term and assortativity
by sex. Note that the network is almost exclusively heterosexual
and there are no male-male edges at all, so the "base" has to
be either (1,3) or (2,3). I'm choosing (1,3) so that the
parameter will be the count of heterosexual edges. This is going
to be highly correlated with the total # of edges, but we have
to have the term in there, otherwise the model will make edges
indiscriminately. 

```{r C5}
```


Plot a simulated version of the network

```{r C6}
```

### Goodness of fit

```{r C7}
```

### Question 8

What is the _conditional_ probability of a 
heterosexual edge?


```{r C8}
```

_Answer here_

## Model 2: Add monogamy term

We see in the goodness of fit data that the model does not
match the network in terms of the number of degree 1 nodes.
So, we add a term to constraint the model to account for these
nodes. Note that base=-2 is the same as base=c(1,3).

```{r C9}
```

### Diagnostics

This fit requires MCMC, so we look at the diagnostics

```{r C10}
```

Not enough mixing of the model. Geweke statistics are poor.

### GOF
```{r C11}
```

Degree distribution is much better.

## Model 3: Model 2 with more computation

Try to improve the fit by
adding more burn-in time and longer interval between samples.

```
# Not run
# Model fit and save code here from C12save
ga.m3 <- ergm(ga.net ~ edges + nodemix("sex", base=-2)+ degree(1),
              control=control.ergm(MCMC.burnin=50000,
                                   MCMC.interval=5000))
```

Load saved model fit

```{r C12load}

```

### Diagnostics. 

Note that the Geweke statistics are better but not
great. Probably we should increase the burn-in even more, but
we won't, in interest of time.

```{r C13}
```

### GOF

```{r C14}
```

## Model 4: Adding age difference

This model is good as far as it goes, but we note that there
is often a tendency to homophily in terms of age in romantic
partners. So, we will try to capture that with an absdiff term.
This creates a statistic for the network which is the sum of
all the absolute differences in ages in all edge pairs. We
already know that longer computation time is required, so
we just keep the ```control``` parameters the same.

```
# Not run
# Model fit and save code here from C15save
ga.m4 <- ergm(ga.net ~ edges + nodemix("sex", base=-2) + degree(1)
              + absdiff("birthyear"),
              control=control.ergm(MCMC.burnin=50000,
                                   MCMC.interval=5000))
```

```{r C15load}

```

### Diagnostics

```{r C16}
```

Note that burn-in diagnostics for birthyear are not that great and that drags the whole thing down. More computation would help.

### Goodness of fit

```{r C17}
```

## Model 5: Differentiating monogamy by sex

AIC went down with the addition of age difference. So, our
model seems pretty good. Let's now try to get at our original
question: how to men and women differ in terms of the number
of partners? We will break up the degree 1 term by sex. I'm
also increasing the sample size to try to get better significance
in the results.

```
# Not run
# Model fit and save code here from C18save
ga.m5 <- ergm(ga.net ~ edges + nodemix("sex", base=-2)
              + degree(1, "sex") + absdiff("birthyear"),
              control=control.ergm(MCMC.burnin=100000,
                                   MCMC.interval=5000,
                                   MCMC.samplesize=2048))
```

```{r C18load}
```

### Diagnostics

```{r C19}
```

### Goodness of fit

```{r C20}

```

Simulated version of the M5 network

```{r C21}
```

This model isn't perfect. It might make sense to add additional
fitting time. We could explore alternatives to the birthyear
term or adding in race, which is a feature available in this
data.

For the purposes of this lab, we'll stop here and see what
we've learned. 

## Analyzing monogamy by sex

We want to look at the probabilities of different kinds of
edges to understand how the network is organized by sex. 

### Model coefficients

```{r  C22}
```

###  Build data frame

 

```{r C23}

```

### Compute conditional probability and sort

```{r C24}

```

### Analysis: 
_The writing in Grey's Anatomy shows interesting biases in the way that romantic relationships form when considering the number of partners previously witnessed on the show for the different individuals who are coming together. The three most likely scenarios which are given by conditional log-odds between 77%-98% all involve a male character who has not been in a relationship yet. This suggests that when a new male character is introduced to the show, they do not remain single for long and end up coupling off with a female character regardless of the number of romantic partners they have had. The inverse of these scenarios (where single female characters link up with male characters) are less likely: the most likely scenario is still the top spot (98% likely) where a single female gets together with a single male, however the next most likely scenarios occur as the 4th most likely (single female gets together with a male with 2+ previous romantic partners is 72% likely) and 7th most likely (single female gets together with a male with only 1 previous romantic parnter). The interesting conclusion from this is that single male characters aren't likely to stay single for very long compared to their single female counterparts (unless they are both single)_

_The 3rd-6th most likely scenarios for romantic coupling all involve a man on the show who has been with 2+ females already getting together with a female of any kind (conditional log-probability range 15%-72%). The likelihood of female characters with 2+ existing partners getting together with another male character are more spread out: the most likely scenario occurs with 92.9% probability and involves that character getting together with a single male. The next most likely is the female with 2+ partners getting together with the man with 2+ partners (40% likely). The final scenario with a 2+ partner female involves getting together with a man of only 1 romantic relationship and only occurs 3% of the time (this is 5x LESS than the inverse with the male). For both genders, the scenario with involving an individual with 2+ romantic partners getting together with a previously single character is the most likely, which may suggest that when new characters are introduced that they are most likely to get together first with a character who gets around more frequently. The "homewrecker" scenario which involves a character with only 1 romantic relationship getting together with another who has a history of more partners is 5x more likely for a male than it is for a female; these seems to suggest that there are more male "homewreckers" in Grey's Anatomy than there are females._

_The three most unlikely romantic coupling scenarios in the show involve males who have one partner (range of probabilities: 0.9%-11%). The least likely scenario in the entire show (0.9%) involves the coupling of a male and female who both have only one partner each. Interstingly, the scenario which involves a male with one partner getting together with a female who has had no romantic partners (11%) is nearly 10x LESS likely than the inverse scenario where a male character with no partners gets togeter with a female character who already has one partner (77%). This suggests a different variant of the "homewrecker" scenario - the "semi-respectable homewrecker" scenario. This is where a new character who has not been romantically involved with anyone else comes along and couples together with an individual who is/was with another person already. This may involve disrupting their relationship in someway (hence the "homewrecker) but is "semi-respectable" (compared to the character who regularly wrecks homes/relationships) because the character hasn't made a habit of this behavior and it is possible that their motives originate from genuine-feelings. This scenario is 10x more likely where the man is the "semi-respectable homewrecker" than for a female character. This is another interesting bias where it seems that male characters are more likely to break up a female characters existing relationship (or swoop in during an existing break-up) than females doing this to a male character's relationship._ 

